---
title: "Readme"
author: "Jarrett Byrnes"
date: "June 8, 2015"
output: md_document
---


```{r}
#Load methods for dealing with data
source("./R/dataGenerationFunctions.R")

#Load the fish data
fish <- read.csv("./data/rawData_SBCfish.csv")
fish <- subset(fish, fish$Year!=2000) #too much variation in this year
```

So, there are differences in # of years sampled from site to site and we want the core set that was sampled in all years filter to sites that are in the whole dataset

```{r}
fishSamples <- fish %>% group_by(Latitude, Longitude, Year) %>%
  summarise(n=n()) %>% ungroup() %>% 
  group_by(Latitude, Longitude) %>%
  summarise(nYearsSampled=n()) %>% 
  ungroup() %>%
  filter(nYearsSampled==max(nYearsSampled))

fishSamples$SampleID <- 1:nrow(fishSamples)
  
#use inner_join to filter down to those sites only
fish <- inner_join(fish, fishSamples)

#we'll need this later
nplots <- length(unique(paste(fish$Latitude, fish$Longitude)))


```


Create a simulated data set where for every scale, there are the same number of observations (total number of transects) and plot it relative to different predictors on the X-axis

Note, getSubData takes the following arguments:
  dataset - the name of a dataset 
  nplots - total number of unique plots
  n - the number of plots that will be used to create a n plot set
  noSpecies="-99999"- the code in the dataset for no species being in a plot
  uniquePerms=T - Only create unique permutations where no plots are shared within set of plots (sampling without replacement)

```{r, echo=FALSE}

simData <- lapply(2:17, function(m) getSubData(fish, nplots, m, sampleframe=fishSamples))
simData <- plyr::ldply(simData)
```

Look at it!
```{r plotTseries}
library(ggplot2)

qplot(Year, Aggregated_Richness, data=simData, group=SampleID, 
      geom="line", color=Bounded_region, facets=~Scale)

qplot(Scale, Aggregated_Richness, data=simData, group=Year, 
      geom="point",size=I(0), color=Year) +
  stat_smooth(fill=NA)

qplot(Bounded_region, Aggregated_Richness, data=simData, group=SampleID, 
      geom="point", color=Scale, facets=~Year)
```

And a sample analysis - although this will get better, right Forest?

```{r analysis}
library(lme4)
library(lmerTest)
#We want to do this, but it won't converge
#mod.full <- lmer(Aggregated_Richness ~ Year*Scale*Bounded_region +
#                   (1+ Year*Scale*Bounded_region|sampleID),
#                 data=simData)


#instead we do this
mod.novarslope.ranef<- lmer(Aggregated_Richness ~ Year*log(Scale)*Bounded_region +
                                   (1+log(Scale)|SampleID),
                                 data=simData)

summary(mod.novarslope.ranef)
```